\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{soul}
\usepackage{amsmath}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Benchmarking anomaly detection techniques in the fraud detection domain*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Leonardo Brito}
    \IEEEauthorblockA{\textit{Engineering and Data Science} \\
        \textit{Instituto Superior Técnico}\\
        Lisbon, Portugal \\
        leonardo.amado.brito@tecnico.ulisboa.pt}
    \and
    \IEEEauthorblockN{Company Supervisor: Jacopo Bono}
    \IEEEauthorblockA{\textit{Data Scientist} \\
        \textit{Feedzai}\\
        Porto, Portugal \\
        jacopo.bono@feedzai.com }
}

\maketitle

\begin{abstract}
    This document is a model and instructions for \LaTeX.
    This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes,
    or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
    component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
In the realm of digital transactions, the significance of detecting fraud at its earliest is paramount. Supervised learning models are often the preferred choice, renowned for their accuracy, but they hinge on the availability of labeled data. This dependency can introduce operational delays, leaving a window where transactions might be exposed to unchecked fraudulent activities.

To address this gap, there's a growing interest in leveraging unsupervised learning. Without the need for labeled data, unsupervised anomaly detection techniques offer a promising avenue, especially when one considers that fraud typically surfaces as statistical anomalies amidst legitimate transactions.

Drawing from open-source datasets, this report sets out to critically evaluate a range of unsupervised anomaly detection methods in the context of fraud detection. Our approach is methodical: starting with a detailed data exploration, we then benchmark against a supervised baseline, and finally, analyze the performance of both classical and deep learning unsupervised models. The overarching aim is to ascertain the potential of unsupervised techniques in offering interim protection against fraud during periods when supervised models are not yet feasible.

\input{EDA.tex}


\section*{References}

Please number citations consecutively within brackets \cite{b1}.

\begin{thebibliography}{00}
    \bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\end{thebibliography}

\end{document}
